Changelog

### 2021-05-24 changelog.tex
Updates from Overleaf

Abacus identifies and quantifies side-channel leakages in a single trace. So it suffers from the problem of code coverage.  That is, Abacus misses side-channel leakages in the unexecuted code path. I have a few choices. I can use static analysis (model checking or static program analysis). Although I am interested in the static analysis, I am not a big fan of current static analysis tools, especially for side-channel analysis. There are several papers on static side-channel analysis. But nearly all of them have high false positive rates. My personal experience with Coverity is similar. It is a commercial static program analysis tool but still generates plenty of false positives.

On the other hand, there are many successful stories

>>>>

There is no real reason for me to choose fuzzing over other methods. It is just my personal choice.

Abacus identifies and quantifies side-channel leakages in a single trace. So it suffers from the problem of code coverage.  That is, Abacus misses side-channel leakages in the unexecuted code path.

I have a few choices. First, I can use static analysis (model checking or static program analysis). Although I am interested in the static analysis, I am not a big fan of current static analysis tools, especially for side-channel analysis. There are several papers on static side-channel analysis. But nearly all of them have high false positive rates. My personal experience with Coverity is similar. It is a commercial static program analysis tool but still generates plenty of false positives.

On the other hand, there are many successful stories with dynamic tools (e.g., SAGE, AFL, Valgrind) in recent years.
